### 2013-05-09 doc/icml2013/theory.tex
Corrections to the tensor whitening lemma
Added flag to optionally include the appendix, with some corresponding fixes

Going forward, we need to lower bound the restricted strong convexity
constant $\kappa(\opX_p)$ and upper bound the operator norm of the adjoint operator
$\|\opX_p^*(\eta_p)\|_\op$. The proofs of the following lemmas follow
from standard concentration inequalities and are detailed in the
supplementary material.
%have been deferred to \appendixref{sec:proofs}.

@@

Having bounded the error of the compound parameter estimates $\hat M_2$ and $\hat M_3$,
we will now study how this error propagates through the tensor factorization step of 
\algorithmref{algo:spectral-experts},
which includes whitening, applying the robust tensor power method \cite{AnandkumarGeHsu2012},
and unwhitening.
\begin{lemma}
  \label{lem:tensorPower} Let $\|\hat M_2 - M_2\|_\op$ and $\|\hat M_3 - M_3\|_\op$ both be less than
  \vspace{-0.5em}
  $$\frac{\sigma_k(M_2)^{5/2}}{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}~ \epsilon,$$
  for some $\epsilon < \half$. 
  Then, there exists a permutation of indices such that  the parameter
  estimates found in step 2 of \algorithmref{algo:spectral-experts}
  satisfy the following with probability at least $1 - \delta$:
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty} &\le \epsilon \\
  %&= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2 &\le \epsilon.
  %&= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{ \sigma_k(M_2)^{5/2} }~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
\end{lemma}

The proof follows by applying standard matrix perturbation results for
the whitening and unwhitening operators and has again been deferred
to the supplementary material.
%\appendixref{sec:proofs}.

>>>>

Going forward, we need to lower bound the restricted strong convexity
constant $\kappa(\opX_p)$ and upper bound the operator norm of the adjoint operator
$\|\opX_p^*(\eta_p)\|_\op$. The proofs of the following lemmas follow
from standard concentration inequalities and are detailed in 
\iftoggle{withappendix}{
\appendixref{sec:proofs:regression}.
}{
the supplementary material.
}
%have been deferred to \appendixref{sec:proofs}.

@@

Having bounded the error of the compound parameter estimates $\hat M_2$ and $\hat M_3$,
we will now study how this error propagates through the tensor factorization step of 
\algorithmref{algo:spectral-experts},
which includes whitening, applying the robust tensor power method \cite{AnandkumarGeHsu2012},
and unwhitening.
\begin{lemma}
  \label{lem:tensorPower}
  Let $M_3 = \sum_{h=1}^{k} \pi_h \beta_h\tp{3}$.
  Let $\|\hat M_2 - M_2\|_\op$ and $\|\hat M_3 - M_3\|_\op$ both be less than
  \vspace{-0.5em}
  $$\frac{\sigma_k(M_2)^{5/2}}{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}~ \epsilon,$$
  for some $\epsilon < \half$. 
  Then, there exists a permutation of indices such that  the parameter
  estimates found in step 2 of \algorithmref{algo:spectral-experts}
  satisfy the following with probability at least $1 - \delta$:
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty} &\le \epsilon \\
  %&= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2 &\le \epsilon.
  %&= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{ \sigma_k(M_2)^{5/2} }~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
\end{lemma}

The proof follows by applying standard matrix perturbation results for
the whitening and unwhitening operators and 
\iftoggle{withappendix}{
can be found in \appendixref{sec:proofs:tensors}.
}{
has again been deferred to the supplementary material.
}
%\appendixref{sec:proofs}.
